Examining Whether Approximate Visualizations Impact Perception of Corrected Visualizations

### 2016-11-14 paper/paper.tex
acks
experimental setup and some other skeleton stuff.

@@

\section{Statistical Analysis}\label{sec:statistical_analysis}

\subsection{Subsection Heading Here}
Subsection text here.

% needed in second column of first page if using \IEEEpubid
%\IEEEpubidadjcol

@@

@@

The authors would like to thank Michael D. Ernst for his feedback on the experimental design and writing.

>>>>

This paper builds from literature on exploring large datasets, visualizing uncertainty, and studies of human perception of visualizations.

I'm punting on this section. Dominik, all you :-)

\subsection{Exploring Large Datasets through Interactive Visualization}

\cite{moritz2017pangloss} \cite{fisher2012trust}

\subsection{Visualizing Uncertainty}

\cite{kay2016ish}

\subsection{Understanding Human Perception of Visualization}

\cite{brehmer2013multi} \cite{heer2010crowdsourcing}
Things like Weber's law, Error Bars Considered Harmful

We sought to create an experiment which mimiced the experience of Exploratory Data Analysis with an approximate query system while still maintaining control over participant experiences.
In approximate query systems, users often internalize approximate visualizations, using the gained knowledge to inform the next visualization to create.
Systems, such as PanGloss \cite{moritz2017pangloss}, can later generate precise visualizations based on the data.
However, the user may have moved on to investigate a new visualization.

Our study flow (Figure X) aimed to mimic this experience. %TODO: add; probably include a few screenshots about what participants actually saw.
Participants viewed two approximate visualizations followed by two precise visualizations.
The study enforced participants view the visualizations for at least 10 seconds before advancing. %TODO: why do we pick 10 seconds?
To ensure that participants had considered the approximate data, we asked a few questions after viewing each approximate visualization informed by Brehmer and Munzner's work \cite{brehmer2013multi}.
Answering these questions simulated how a data analyst would consider and reflect on their data.
The questions also provided us a baseline level of comprehension of visualizations of our participants.
After viewing both precise visualizations, participants answered a larger set of questions based on Brehmer and Munzner's work \cite{brehmer2013multi}.
Participants were asked to rate their confidence in their answer to each question in both sets on a sliding scale from "I don't remember" to "I'm certain".
Participants were informed that first two visualizations were approximations of their data, allowing us to mimic the experience of looking at an approximate query result.
%Do we want to go into more detail on the questions? In a 'dependent variables' section?

The two visualizations participants saw were based on the same dataset about flights in the United States. \url{http://datahub.io/dataset/open-flights}
Both visualizations were bar graphs, which are common in approximate query systems \cite{moritz2017pangloss}.
The y-axis varied between the two visualizations, showing either the state the flight left from or the airline of the flight.
The x-axis in both visualization was a count value.

Participants were recruited from Amazon Mechanical Turk (AMT).
Similar to other studies of human perception of visualizations, we restricted participation to people on AMT with at least 1,000 tasks completed and an approval rate above 95\%.
Participation was restricted to the United States to ensure familiarity with the airlines and states in the dataset.
Participants were compensated \$2.00 for completing the study.

\subsubsection{Independent Variables}

%Probably make a figure for this too.
We evaluated three techniques for presenting the precise visualization.
Our control condition presented just the updated, precise data, as in PanGloss and other systems \cite{moritz2017pangloss}.
We further tested presenting the approximate and precise visualizations side-by-side, and a visualization highlighting the approximate data on the precise visualization.

We varied how much of the dataset was sampled for each approximate visualization.
We tested sample levels of 0.1\%, 0.2\%, 0.5\%, and 1\%, with an additional control condition of 100\% (e.g., the approximate visualization was identical to the precise visualization).
Smaller samples tended to have greater difference from the precise visualizations.
For each approximate visualization, we recorded the difference from the precise visualization relative to the questions we asked.
For example, if a participant was asked "How many flights were there on Alaska Airlines?", we record the difference in flights between the approximate and precise visualization.

We randomized visualization order, approximate sample, and study condition for each participant.
As previously stated, the variation level of the approximate visualizations varied by visualization.

\subsection{Statistical Analysis}

@@

\section{Results}\label{sec:results}

@@

\section{Discussion}\label{sec:discussion}

Tie to crowdsourcing literature here, about what our work could inform over there.

\subsubsection{Threads to Validity} %I would opt to put this under the experimental setup, but I understand that Mike might want differently.

We had no way of ensuring that participants did not take screenshots in order to answer later questions about the precise visualizations.

@@

The authors would like to thank Michael D. Ernst for his feedback on the experimental design and writing.
They would also like to thank Jessica Hullman and Danyel Fisher for their feedback on the study design and research questions.
